The promise of community-driven preprints in ecology and evolution

### 2024-05-03 ms/ms.qmd
Small fixes

*EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary biology (SORTEE)[@o2021towards]. Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolutionary biology. It has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees. Editors are researchers from across the globe (currently eight different countries) in the fields of ecology and evolutionary biology who volunteer their time to screen papers and push new initiatives in the preprint space. *EcoEvoRxiv* accepts both preprints and postprints, or author-accepted manuscripts (AAM) -  a version of an accepted or published article without typesetting and formatting by a journal. Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints-- though most do; see https://www.sherpa.ac.uk/romeo/). To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods). For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints as 'articles' in our overview analysis.

>>>>

*EcoEvoRxiv* is run by the Society for Open, Reliable, and Transparent Ecology and Evolutionary biology (SORTEE)[@o2021towards]. Originally launched in 2018 on the Center for Open Science preprint platform, *EcoEvoRxiv* has grown to become a popular preprint server for researchers in ecology and evolutionary biology. It has since been adopted by the California Digital Library (CDL) to be hosted in perpetuity without fees. Editors are researchers from across the globe (currently eight different countries) in the fields of ecology and evolutionary biology who volunteer their time to screen papers and push new initiatives in the preprint space. *EcoEvoRxiv* allows authors to post both preprints and postprints, or author-accepted manuscripts -  a version of an accepted or published article without typesetting and formatting by a journal. Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy that recognises preprints-- though most do; see https://www.sherpa.ac.uk/romeo/). To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])` (see Supplement for more details on methods). For the purpose of summarising articles on *EcoEvoRxiv* we include both preprints and postprints as 'articles' in our overview analysis.
